---
title: "index"
author: "Alex Filazzola"
date: "March 16, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r warning=FALSE, message=FALSE}
library(raster)
library(rgdal)
library(dismo)
library(rJava)
library(maptools)
library(rgeos)
library(MASS)
```

### download species location
```{r}

# Genus <- "Ephedra"
# temp <- gbif(Genus, geo=T) ## all ephedra individuals that have lat& long
# temp <- subset(temp, country=="United States") ## all ephedra instances in the US
# temp<-na.omit(temp[,c("lon","lat","species")]) ## extract lat long and species name. Complete cases only
# temp <- temp[!duplicated(temp), ] ## remove duplicates
# write.csv(temp, "ephedra.locations.USA.csv")
ephedra <- read.csv("data\\ephedra.locations.USA.csv")

## get USA boundaries
USA1 <- getData('GADM' , country="USA", level=1)# use state bounds from gadm website:
## get California outline
cal<- c("California") ## extract states (need to uppercase everything)
cal = USA1[match(toupper(cal),toupper(USA1$NAME_1)),]
```

###download aridity index raster
```{r}

## Aridty calculated using Precipitation/Potential Evapotranspiration from Maliva, R., & Missimer, T. (2012). Aridity and drought. In Arid lands water evaluation and management (pp. 21-39). Springer Berlin Heidelberg.

## Online aridity dataset created by Zomer et al. 2007 & 2008 - http://www.cgiar-csi.org/data/global-aridity-and-pet-database


global.AR <- raster("global.AR.tif")


```

### extract aridity from ephedra locations in California
```{r}

## convert facilitated occurrence into spatial points
gps <- ephedra[,2:3]
crs.world <-CRS("+proj=longlat +datum=WGS84")
coordinates(gps) <- ~lon+lat
proj4string(gps) <- crs.world

##crop out points to California only
gps <- crop(gps, extent(cal))
samplearea <- circles(gps, d=5000, lonlat=T)


## sample points
backgr <- spsample(samplearea@polygons, 1000, type='random', iter=99)

##extract aridity
aridity.data <- extract(global.AR, backgr)


## aridity gradient
hist1 <- hist(subset(aridity.data, aridity.data<5000), breaks=20)

```
### site aridity 

```{r}
site.names <- c("Panoche","Cuyama","Barstow","MojavePreserve","SheepholeValley","Tecopa","TejonRanch")
site.lat <- c(36.70000998,34.85521998,35.094051,34.698199,34.205676,35.85151504,34.875994)
site.lon <- c(-120.801116,-119.48851,-116.8349,-115.684169,-115.719676,-116.186706,-118.60246)

## turn sites into spatial points
sites <- data.frame(site.names,site.lon,site.lat)
sites <- SpatialPoints(sites[,2:3])
proj4string(sites) <- crs.world

## extract aridity of spatial points
aridity.sites <- extract(global.AR, sites)

match.vals <- function(x) {which(abs(hist1$mids-x)==min(abs(hist1$mids-x)))} ## find the aridity values that are already used in the study
covered <- unique(sapply(aridity.sites, match.vals))
test <- hist1$mids[covered]## aridity values that are currently being used
colours <- match(hist1$breaks,test+100)
colours <- ifelse(is.na(colours),0,8)

hist1 <- hist(subset(aridity.data, aridity.data<5000), breaks=20, col=colours, main="", xlab="aridity")
legend(3700,100, c("unsampled","sampled"), pch=22, pt.bg=c(0,8))

```

### identify areas that are missing
```{r}


## extract sites with unsampled aridity values
missing.eph <-  extract(global.AR, gps)

missing.eph <- SpatialPointsDataFrame(coords=gps, data=data.frame(missing.eph))

missing.vals <- data.frame(aridity=c(hist1$breaks),colours)
missing.vals[missing.vals$colours==0,"aridity"]
```

```{r warning=FALSE, message=FALSE}
library("leaflet")

plot.ranges <- function(x1,x2){
new.points <- subset(missing.eph, missing.eph>x1 & missing.eph<x2)
(m <- leaflet() %>% addTiles())
(m %>% setView(lng = -118, lat = 35, zoom = 6)  %>%   addMarkers(new.points, lng=new.points@coords[,1],lat=new.points@coords[,2], popup=new.points$missing.eph, label=as.character(new.points$missing.eph)))
}

plot.ranges(1400,1600)
plot.ranges(1600,1800)
plot.ranges(1800,2000)
plot.ranges(2000,2200)
plot.ranges(2200,2400)
plot.ranges(2400,2600)